Forecasting the 2024 U.S. Presidential Election: Polling Trends and Dynamics Based on National General Election Polls

### 2024-11-04 paper/paper.qmd
added NTY reference

---
title: "Forecasting the 2024 U.S. Presidential Election"
author: 
  - Jason Yang
  - Jerry Xia 
  - Peter Fan
thanks: "Code and data are available at: [https://github.com/Jerryx2020/US_election_prediction/tree/main]."
date: "`r format(Sys.Date() - 1, '%A, %B %d, %Y')`" #chatgpt assisted how to create a custom date for due date November 4
date-format: long
abstract: ""
format: pdf
header-includes: 
  - \usepackage{pdfpages}
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Forecasting the 2024 U.S. Presidential Election: Polling Trends and Dynamics Based on National General Election Polls"
subtitle: "Trump Consistently Leads in National Polls, with Harris Showing Sporadic Gains in Certain Polling Periods"
author: 
  - Jason Yang
  - Jerry Xia 
  - Peter Fan
thanks: "Code and data are available at: <https://github.com/Jerryx2020/US_election_prediction/tree/main>."
date: today
date-format: long
abstract: ""
format: pdf
header-includes: 
  - \usepackage{pdfpages}
number-sections: true
bibliography: references.bib
---
